Lawvere-Tierney Sheafification\\ in Homotopy Type Theory

### 2016-01-19 paper/paper_acm.tex
typo

Technically, Lawvere-Tienrey sheafification in homotopy type theory
allows to construct a model of homotopy type theory (with only one
universe) with new logical principles (such as EM) from a model of
homotopy type theory.

>>>>

Technically, Lawvere-Tierney sheafification in homotopy type theory
allows to construct a model of homotopy type theory (with only one
universe) with new logical principles (such as EM) from a model of
homotopy type theory.
